\chapter{Implementation}

\section{Program Modules and Functions}
\begin{itemize}
    \item \textbf{Auth Module:} Handles JWT issuance, password hashing, and middleware validation.
    \item \textbf{Ledger Service:} Enforces double-entry rules. It handles deposits, fees, and cross-account transfers by generating paired debit/credit journal lines.
    \item \textbf{Transfer Coordinator:} Manages the Maker/Checker state machine and the complex 2PC execution across the FDW-linked databases.
    \item \textbf{Compliance Module:} Manages KYC tracking and surfaces the visual badges to the Next.js UI, alongside the \texttt{auditRouter} for tracking administrative actions.
\end{itemize}

\section{Member Specific Implementation}
\textit{(To be filled by students. Ensure contributions are unique.)}

\subsection{Member 1: Anosh}
\textbf{Contribution Details:} 
\begin{itemize}
    \item Configured the Docker environment and PostgreSQL 2PC/FDW topology.
    \item Implemented the core Ledger Service and Idempotency middleware.
    \item Developed the Next.js frontend dashboard and transfer approval UI.
\end{itemize}

\subsection{Member 2: [Name Here]}
\textbf{Contribution Details:}
\begin{itemize}
    \item Designed and implemented the Compliance (KYC) database joins and Audit Trail endpoints.
    \item Developed the \texttt{seed\_demo.ts} scripts for automated testing and environment provisioning.
    \item Handled the backend authentication logic and role-based access control (RBAC).
\end{itemize}
